---
title: "test for hw1"
author: "Yige Bian"
date: 2023-9-18
output: 
  html_document:
    toc: true
    toc_float: true
    theme: flatly
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    code_folding: hide
---

```{r setup, include = FALSE}
library(tidyverse)
```

# Problem 1
```{r data initialize}
library(moderndive)
data("early_january_weather")
```

The dataset 'early_january_weather' has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. Variables in the dataset are `r colnames(early_january_weather)`.

*   The variable `origin` has class `r class(pull(early_january_weather, origin))`
*   The variable `year` has class `r class(pull(early_january_weather, year))`
*   The variable `month` has class `r class(pull(early_january_weather, month))`
*   The variable `day` has class `r class(pull(early_january_weather, day))`
*   The variable `hour` has class `r class(pull(early_january_weather, hour))`
*   The variable `temp` has class `r class(pull(early_january_weather, temp))`
*   The variable `dewp` has class `r class(pull(early_january_weather, dewp))`
*   The variable `humid` has class `r class(pull(early_january_weather, humid))`
*   The variable `wind_dir` has class `r class(pull(early_january_weather, wind_dir))`
*   The variable `wind_speed` has class `r class(pull(early_january_weather, wind_speed))`
*   The variable `wind_gust` has class `r class(pull(early_january_weather, wind_gust))`
*   The variable `precip` has class `r class(pull(early_january_weather, precip))`
*   The variable `pressure` has class `r class(pull(early_january_weather, pressure))`
*   The variable `visib` has class `r class(pull(early_january_weather, visib))`
*   The variable `time_hour` has class `r class(pull(early_january_weather, time_hour))`.

The mean temperature is `r mean(pull(early_january_weather, temp))`

```{r scatter plot for time and temp}
Sys.setlocale("LC_TIME", "English")
ggplot(early_january_weather, aes(x = time_hour, y = temp, color=humid)) + geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 6)
```

The scatter plot illustrates that, from January 1st to January 15th, a noticeable upward trend in temperature fluctuations can be observed. The temperature during different times of the day follows a similar pattern of change, and overall, the average temperature continues to rise. In the first few days of January, the humidity is relatively low. Starting from January 6th, there are intermittent periods of increased humidity. It's worth noting that from January 11th to January 14th, the humidity is particularly high, and during these days, the daily temperature fluctuations are relatively small.

# Problem 2
```{r data initialize for problem2}
set.seed(1)

samp_df = tibble(
  vec_random = rnorm(10),
  vec_logical = vec_random > 0,
  vec_char = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
  vec_factor = factor(c("high", "med", "samll", "high", "med", "med", "samll", "samll", "high", "med"))
)
```

```{r}
mean(pull(samp_df,vec_random))
mean(pull(samp_df,vec_logical))
mean(pull(samp_df,vec_char))
mean(pull(samp_df,vec_factor))
```
```{r}
mean(as.numeric(pull(samp_df,vec_char)))
as.numeric(pull(samp_df,vec_factor))
```




