---
title: "test for hw1"
author: "Yige Bian"
date: 2023-9-18
output: github_document
---

```{r setup, include = FALSE}
Sys.setlocale("LC_TIME", "English") # Manually change the language into English due to the limitation of windows license
library(tidyverse)
```

# Problem 1
## Data description
```{r data initialization}
# Load the moderndive library and load the early_january_weather datase
library(moderndive)
data("early_january_weather")
```

*   Variables in the dataset 'early_january_weather' are `r colnames(early_january_weather)`.
    *   The variable `origin` has class `r class(pull(early_january_weather, origin))`
    *   The variable `year` has class `r class(pull(early_january_weather, year))`
    *   The variable `month` has class `r class(pull(early_january_weather, month))`
    *   The variable `day` has class `r class(pull(early_january_weather, day))`
    *   The variable `hour` has class `r class(pull(early_january_weather, hour))`
    *   The variable `temp` has class `r class(pull(early_january_weather, temp))`
    *   The variable `dewp` has class `r class(pull(early_january_weather, dewp))`
    *   The variable `humid` has class `r class(pull(early_january_weather, humid))`
    *   The variable `wind_dir` has class `r class(pull(early_january_weather, wind_dir))`
    *   The variable `wind_speed` has class `r class(pull(early_january_weather, wind_speed))`
    *   The variable `wind_gust` has class `r class(pull(early_january_weather, wind_gust))`
    *   The variable `precip` has class `r class(pull(early_january_weather, precip))`
    *   The variable `pressure` has class `r class(pull(early_january_weather, pressure))`
    *   The variable `visib` has class `r class(pull(early_january_weather, visib))`
    *   The variable `time_hour` has class `r class(pull(early_january_weather, time_hour))`.
*   The dataset 'early_january_weather' has `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns. 
*   The mean temperature is `r mean(pull(early_january_weather, temp))`

## Data plot
```{r scatter plot for time and temp}
# Scatterplot of temp (y) vs time_hour (x), color points using the humid
ggplot(early_january_weather, aes(x = time_hour, y = temp, color=humid)) + geom_point()
```

The scatter plot illustrates that, from January 1st to January 15th, a noticeable upward trend in temperature fluctuations can be observed. The temperature during different times of the day follows a similar pattern of change, and overall, the average temperature continues to rise. In the first few days of January, the humidity is relatively low. Starting from January 6th, there are intermittent periods of increased humidity. It's worth noting that from January 11th to January 14th, the humidity is particularly high, and during these days, the daily temperature fluctuations are relatively small.

```{r scatterplot export}
# Export scatterplot to project directory
ggsave("scatter_plot.pdf", height = 4, width = 6)
```


# Problem 2
## Dataframe initialization
```{r data initialization for problem2}
set.seed(1)

samp_df = tibble(
  vec_random = rnorm(10),
  vec_logical = vec_random > 0,
  vec_char = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10"),
  vec_factor = factor(c("high", "med", "samll", "high", "med", "med", "samll", "samll", "high", "med"))
)
```
## Mean of variables
```{r}
mean(pull(samp_df,vec_random))
mean(pull(samp_df,vec_logical))
mean(pull(samp_df,vec_char))
mean(pull(samp_df,vec_factor))
```
From the output, we can observe that the variable `vec_random` and `vec_logical` with numeric and logical form could be calculated the mean, while the other two variables `vec_char` and `vec_factor` with character and factor form got the result of NA and encounter the warning: argument is not numeric or logical.

## Convert of variable types
```{r, eval = FALSE}
# Define variables with different data type
samp_num = c(-1, 1, 0.4, -3, 4)
samp_logical = samp_num < 0
samp_char_str = c("1", "2", "3", "4", "5")
samp_char_num = c("a", "b", "c", "d", "e")
samp_fac_str = factor(c("high", "med", "samll", "high", "med", "med"))
samp_fac_num = factor(c("500", "400", "300", "200", "100", "600"))
samp_fac_mix = factor(c("500", "a", "*", "200", "z", "#"))

# use as.numeric() to convert type of variables
as.numeric(samp_logical)
as.numeric(samp_char_str)
as.numeric(samp_char_num)
as.numeric(samp_fac_str)
as.numeric(samp_fac_num)
as.numeric(samp_fac_mix)
as.numeric(as.character(samp_fac_num))
```
We have defined variables `samp_logical` with class `logical`, `samp_char_str` with class `character`, `samp_char_num` with class `character`, `samp_fac_str` with class `factor`, `samp_fac_num` with class `factor` and `samp_fac_mix` with class `factor`.

1.    Logical variable: we observed that under the function `as.numeric()`, true value will be converted to 1 and false value will be converted to 0. 
2.    Character variable: if the variable stored numbers in char type like `samp_char_num`, as.numeric() could convert it into numeric, while if the variable stored string in char type like `samp_char_str`, as.numeric() will fail to convert it to numeric.
3.    Factor variable: We observed that when use as.numeric() to convert factor to numeric, it will be converted to number from 1 to n follows some rules of rank, where n is the number of different values in the variable. If all values are numbers like `samp_fac_num`, the rank is the value of number from small to large. If all values are strings like `samp_fac_str`, the rank is the alphabetic sequence. If values in the variable are a mix of numbers, strings and symbols like `samp_fac_mix`, it follows the rank symbol, number and string. Moreover, if we want to obtian the number in `samp_fac_num` into numeric type, we should use `as.character()` to convert it to char first, and then use `as.numeric()` to convert it to numeric.